DataGatheringandAnalysis

### 2014-11-11 GEMDataSource.Rmd
Update 11/11

@@

# Run a linear regression
R1 <- lm(PercentNascent ~ PercentPerceived + PercentIntention, data = FinalMerge)
summary(R1)

@@

```

>>>>

# Install rempis from Christpher Gandrud's website

@@

# Run a linear regression
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear, data = FinalMerge)
summary(R1)

@@

# Run a linear regression
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalMerge)
summary(R2)

# Calculate confidence intervals
confint(R2)

# Run a linear regression
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalMerge)
summary(R3)

# Calculate confidence intervals
confint(R3)

# Plot graph
car::scatterplotMatrix(FinalMerge)
```
